---
title: "Binomial Distribution"
output: html_notebook
---

Binomial distribution 

```{r}
require('ggplot2')

x <- c(0:10)
y <- dbinom(x, size=10, .5, log = FALSE)

qplot(x, y, color = I("green"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

the Pascal triangle starts with:
            x = 0
         size = 0
 the density  = 1 (the vertex of the triangle)

 then we are moving to:
            x = c(0:1)
         size = 1       //one sample from the choise of two- 0 and 1
 the density  = 0.5, 0.5
 ...
            x = c(0:n)
         size = n
  probability = p

The thing that is freequently being forgotten is the way it behaves in asymmetric case, when the probability of a 'positive' outcome shifts towards 0 or 1.

```{r}
y <- dbinom(x, size=10, .75, log = FALSE)

qplot(x, y, color = I("red"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

and

```{r}
y <- dbinom(x, size=10, .25, log = FALSE)

qplot(x, y, color = I("magenta"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```


The formula is


```{r}
#dbinom formula (the function is in C)

dbin <- function(x, size, p) {
    d <- choose(size, x)*p^x*(1-p)^(size-x)
}

y <- dbin(x, size=10, .25)

qplot(x, y, size = I(2), color = I("magenta")) +geom_line(size =1, alpha =.5, color="red")
```

