---
title: "Hypergeometric Distribution"
output: html_notebook
---

Hypergeometric distribution

k balls 
# taken without replacement from an urn with

m white balls and
n black balls 
# (all in all- m+n)

x or q  (from the interval [0 - k] )
#is the number of white balls in the sample
                      
                   m        n       m+n
P( x, k, m, n) = (   ) * (     )/ (     )
                   x       k-x       k


```{r}
require('ggplot2')

m <- 5 ; n <- 5
k <- 10

x <- c(0:10)
y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("red"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

Which is totally logical. We drew ALL the balls, 5 of them are white, 5 - black, the probability of 5 white balls is = 1


Let's eliminate the effect of removal by increasing the overall number of balls in the urn but keep the proportion the same

```{r}
m <- 1000 ; n <- 1000
k <- 10

y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("green"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

Exactly the same as the Binomial distribution with size = 10 and p=0.5 .

Now let's dampen the effect of removal gradually

```{r}
m <- 6 ; n <- 6
k <- 10

y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("steelblue"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

only the neighbours of the central point are nonzero

```{r}
m <- 8 ; n <- 8
k <- 10

y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("blue"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

On and on it goes...

```{r}
m <- 10 ; n <- 10
k <- 10

y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("green"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

10 white and 10 black, sample 10 still much sharper than the Binomial with size 10 and p=0.5

Now let's move it to the sides in the case when the effect of removal is still visible

```{r}
m <- 15 ; n <- 5
k <- 10

y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("red"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

```{r}
m <- 5 ; n <- 15
k <- 10

y <- dhyper(x, m, n, k, log = FALSE)

qplot(x, y, color = I("magenta"), 
      size = I(2), alpha = I(1/2), geom = c("point"))
```

Hypergeometric is just MUCH sharper if the numbers are comparable.


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
